Quality measure notes

### 2021-09-07 StateOfPractice/Ao-Report/16AnswersToResearchQuestions.tex
MI report - updated ch 8 and more
MI report - updated ch 6

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Artifact & Number of projects \\ \hline
Source code & 29 \\
Version Control & 29 \\
README & 29 \\
License & 28 \\
Bug tracker & 28 \\
Change request & 28 \\
User Manual & 22 \\
Release notes & 22 \\
Build file & 18 \\
Tutorials & 18 \\
Makefile & 18 \\
Installation Guide & 16 \\
Test cases & 15 \\
Authors & 14 \\
FAQ & 14 \\
Acknowledgements & 12 \\
Executable files & 10 \\
Developer's Manual & 8 \\
API documentation & 7 \\
Troubleshooting guide & 6 \\
Project Plan & 5 \\ \hline
\end{tabular}
\caption{\label{tab_artifacts_frequency}Artifacts by their frequency in the 29 MI projects}
\end{table}

@@

Table \ref{tab_ranking_vs_GitHub} shows our ranking to the 29 MI projects, and their GitHub metrics if applicable, in the descending order of the average number of new stars. As mentioned in Section \ref{sec_score_maintainability}, 24 projects used GitHub. Since GitHub repositories have different creation dates, we collect the number of months each stayed on GitHub, and calculate the average number of new stars, people watching, and forks per 12 months. The method of getting the creation date is described in Section \ref{sec_empirical_measurements}, and we obtained these metrics in July, 2021.

Generally speaking, most of the top-ranking MI software projects also received greater attention and popularity on GitHub. Project \textit{dwv} was popular on GitHub, but we ranked it low. As mentioned in Section \ref{sec_result_installability}, we failed to build it locally, and used the test version on its websites for the measurements. We followed the instructions and tried to run the command ``yarn run test" locally, which did not work. In addition, the test version did not detect a broken DICOM file and displayed a blank image as described in Section \ref{sec_result_robustness}. We might underestimate the scores for \textit{dwv} due to uncommon technical issues. We also ranked \textit{DICOM Viewer} much lower than its popularity. As mentioned in Section \ref{sec_result_installability} it depended on the NextCloud platform that we could not successfully install. Thus, we might underestimate the scores of its \textit{surface reliability} and \textit{surface robustness}. We weighted all qualities equally, which is not likely to be the case with all users. As a result, some projects with high popularity may not perform well in all qualities.

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[H]
\centering
\begin{tabular}{lllll}
\hline
Software & Our ranking & Stars/yr & Watches/yr & Forks/yr \\ \hline
3D Slicer & 1 & 284.25 & 18.75 & 128.25 \\
OHIF Viewer & 3 & 277.04 & 19.3 & 223.83 \\
dwv & 23 & 123.56 & 11.59 & 51.36 \\
ImageJ & 2 & 83.58 & 9.37 & 30 \\
ParaView & 5 & 66.76 & 7.11 & 28.36 \\
Horos & 12 & 48.62 & 9.23 & 18 \\
Papaya & 17 & 44.7 & 4.84 & 19.71 \\
Fiji & 4 & 44.2 & 4.98 & 20.68 \\
DICOM Viewer & 29 & 42.86 & 5.71 & 8.57 \\
INVESALIUS 3 & 10 & 39.66 & 4.11 & 17.37 \\
Weasis & 6 & 36 & 5.1 & 18.9 \\
dicompyler & 26 & 35.18 & 4.77 & 13.64 \\
OsiriX Lite & 9 & 34.14 & 8.62 & 23.77 \\
MRIcroGL & 18 & 23.63 & 3.38 & 3.38 \\
GATE & 25 & 18.9 & 5.79 & 25.79 \\
Ginkgo CADx & 14 & 18.83 & 4.43 & 5.72 \\
BioImage Suite Web & 8 & 17.85 & 4.62 & 6.77 \\
Drishti & 27 & 16.04 & 3.78 & 4.43 \\
Slice:Drop & 20 & 9.73 & 2.16 & 4.97 \\
ITK-SNAP & 15 & 9.1 & 0.97 & 3.59 \\
medInria & 7 & 7.04 & 3.35 & 6.35 \\
SMILI & 13 & 3.04 & 0.91 & 1.52 \\
MatrixUser & 28 & 2 & 0.33 & 0.33 \\
MicroView & 16 & 1.48 & 0.82 & 0.82 \\
Gwyddion & 11 & n/a & n/a & n/a \\
XMedCon & 19 & n/a & n/a & n/a \\
DicomBrower & 21 & n/a & n/a & n/a \\
AMIDE & 22 & n/a & n/a & n/a \\
3DimViewer & 24 & n/a & n/a & n/a \\ \hline
\end{tabular}
\caption{\label{tab_ranking_vs_GitHub}Software ranking versus GitHub metrics}
\end{table}
\endgroup

@@

As shown in Section \ref{sec_mi_software_selection}, our domain experts recommended a list of top software with 12 software products. Table \ref{tab_top_software_vs_experts} compares the top 12 software projects ranked by our methodology with the ones from the domain experts.

An example of interpreting Table \ref{tab_top_software_vs_experts} is as follows: in row 2, \textit{ImageJ} has rank 2 by our assessment, and the number \textit{(3)} means that it has rank 3 by the experts; likewise, \textit{Horos} has rank 2 by the domain experts, and rank 12 by our assessment.

@@

\begin{table}[H]
\centering
\begin{tabular}{lll}
\hline
Rank & This assessment & Domain expert \\ \hline
1 & 3D Slicer (1) & 3D Slicer (1) \\
2 & ImageJ (3) & Horos (12) \\
3 & OHIF Viewer (n/a) & ImageJ (2) \\
4 & Fiji (4) & Fiji (4) \\
5 & ParaView (n/a) & AFNI (n/a) \\
6 & Weasis (n/a) & FSL (n/a) \\
7 & medInria (n/a) & Freesurfer (n/a) \\
8 & BioImage Suite Web (n/a) & Mricron (18*) \\
9 & OsiriX Lite (n/a) & Mango (17**) \\
10 & INVESALIUS 3 (n/a) & Tarquin (n/a) \\
11 & Gwyddion (n/a) & Diffusion Toolkit (n/a) \\
12 & Horos (2) & MRItrix (n/a) \\ \hline
\end{tabular}
\caption{\label{tab_top_software_vs_experts}Top software versus domain experts' recommendation}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
Artifact & Number of projects \\ \hline
README & 29 \\
Version Control & 29 \\
License & 28 \\
Bug tracker & 28 \\
Change request & 28 \\
User Manual & 22 \\
Release notes & 22 \\
Build file & 18 \\
Tutorials & 18 \\
Installation Guide & 16 \\
Test cases & 15 \\
Authors & 14 \\
FAQ & 14 \\
Acknowledgements & 12 \\
Executable files & 10 \\
Developer's Manual & 8 \\
API documentation & 7 \\
Troubleshooting guide & 6 \\
Project Plan & 5 \\ \hline
\end{tabular}
\caption{\label{tab_artifacts_frequency}Artifacts by their frequency in the 29 MI projects}
\end{table}

We summarized the definitions of the artifacts in \hyperlink{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Artifacts_MiningV3.xlsx}{https://github.com/.../Artifacts\_MiningV3.xlsx}. Source code is a type of artifact. Since we only included OSS on the final list (Section \ref{sec_mi_software_selection}), every project's source code was available. Thus, we excluded it in the above table.

@@

Table \ref{tab_ranking_vs_GitHub} shows our ranking to the 29 MI projects, and their GitHub metrics if applicable. As mentioned in Section \ref{sec_score_maintainability}, 24 projects used GitHub. Since GitHub repositories have different creation dates, we collect the number of months each stayed on GitHub, and calculate the average number of new stars, people watching, and forks per 12 months. The method of getting the creation date is described in Section \ref{sec_empirical_measurements}, and we obtained these metrics in July, 2021.

In Table \ref{tab_ranking_vs_GitHub}, we used the average number of new stars per 12 months as an indicator of the GitHub popularity, and listed the items in the descending order of this number. We ordered the non-GitHub items by our ranking. Generally speaking, most of the top-ranking MI software projects also received greater attention and popularity on GitHub. Between our ranking and the GitHub stars-per-year ranking, four of the top five software projects are the same.

Project \textit{dwv} was popular on GitHub, but we ranked it low. As mentioned in Section \ref{sec_result_installability}, we failed to build it locally, and used the test version on its websites for the measurements. We followed the instructions and tried to run the command ``yarn run test" locally, which did not work. In addition, the test version did not detect a broken DICOM file and displayed a blank image as described in Section \ref{sec_result_robustness}. We might underestimate the scores for \textit{dwv} due to uncommon technical issues. We also ranked \textit{DICOM Viewer} much lower than its popularity. As mentioned in Section \ref{sec_result_installability} it depended on the NextCloud platform that we could not successfully install. Thus, we might underestimate the scores of its \textit{surface reliability} and \textit{surface robustness}. We weighted all qualities equally, which is not likely to be the case with all users. As a result, some projects with high popularity may not perform well in all qualities.

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[H]
\centering
\begin{tabular}{lllll}
\hline
Software & Our ranking & Stars/yr & Watches/yr & Forks/yr \\ \hline
3D Slicer & 1 & 284 & 19 & 128 \\
OHIF Viewer & 3 & 277 & 19 & 224 \\
dwv & 23 & 124 & 12 & 51 \\
ImageJ & 2 & 84 & 9 & 30 \\
ParaView & 5 & 67 & 7 & 28 \\
Horos & 12 & 49 & 9 & 18 \\
Papaya & 17 & 45 & 5 & 20 \\
Fiji & 4 & 44 & 5 & 21 \\
DICOM Viewer & 29 & 43 & 6 & 9 \\
INVESALIUS 3 & 10 & 40 & 4 & 17 \\
Weasis & 6 & 36 & 5 & 19 \\
dicompyler & 26 & 35 & 5 & 14 \\
OsiriX Lite & 9 & 34 & 9 & 24 \\
MRIcroGL & 18 & 24 & 3 & 3 \\
GATE & 25 & 19 & 6 & 26 \\
Ginkgo CADx & 14 & 19 & 4 & 6 \\
BioImage Suite Web & 8 & 18 & 5 & 7 \\
Drishti & 27 & 16 & 4 & 4 \\
Slice:Drop & 20 & 10 & 2 & 5 \\
ITK-SNAP & 15 & 9 & 1 & 4 \\
medInria & 7 & 7 & 3 & 6 \\
SMILI & 13 & 3 & 1 & 2 \\
MatrixUser & 28 & 2 & 0 & 0 \\
MicroView & 16 & 1 & 1 & 1 \\
Gwyddion & 11 & n/a & n/a & n/a \\
XMedCon & 19 & n/a & n/a & n/a \\
DicomBrower & 21 & n/a & n/a & n/a \\
AMIDE & 22 & n/a & n/a & n/a \\
3DimViewer & 24 & n/a & n/a & n/a \\ \hline
\end{tabular}
\caption{\label{tab_ranking_vs_GitHub}Software ranking versus GitHub metrics}
\end{table}
\endgroup

@@

As shown in Section \ref{sec_mi_software_selection}, our domain experts recommended a list of top software with 12 software products. Table \ref{tab_top_software_vs_experts} and \ref{tab_experts_vs_top_software} compare the top 12 software projects ranked by our methodology with the ones from the domain experts.

@@

\begin{table}[H]
\centering
\begin{tabular}{lll}
\hline
Our ranking & Assessed software & Domain experts \\ \hline
1 & 3D Slicer & 1 \\
2 & ImageJ & 3 \\
3 & OHIF Viewer & n/a \\
4 & Fiji & 4 \\
5 & ParaView & n/a \\
6 & Weasis & n/a \\
7 & medInria & n/a \\
8 & BioImage Suite Web & n/a \\
9 & OsiriX Lite & n/a \\
10 & INVESALIUS 3 & n/a \\
11 & Gwyddion & n/a \\
12 & Horos & 2 \\ \hline
\end{tabular}
\caption{\label{tab_top_software_vs_experts}Top software by our ranking versus domain experts' recommendation}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\hline
Our ranking & Recommended software & Domain experts \\ \hline
1 & 3D Slicer & 1 \\
12 & Horos & 2 \\
2 & ImageJ & 3 \\
4 & Fiji & 4 \\
n/a & AFNI & 5 \\
n/a & FSL & 6 \\
n/a & Freesurfer & 7 \\
18* & Mricron & 8 \\
17** & Mango & 9 \\
n/a & Tarquin & 10 \\
n/a & Diffusion Toolkit & 11 \\
n/a & MRItrix & 12 \\ \hline
\end{tabular}
\caption{\label{tab_experts_vs_top_software}Domain experts' recommendation versus our ranking}
\end{table}
